Missing data: Current practice in football research and recommendations for

### 2020-10-09 paper/paper.Rmd
small changes in paper

# Impute missing values
data_impute <- ampute(data = data[,1:3])
data_with_missing <- data_impute$amp

@@

aq_miss_var <- gg_miss_var(data_plot) + labs(title = "A")
aq_miss_case <- gg_miss_case(data_plot) + labs(title = "B")
aq_vis_miss <- vis_miss(data_plot) + labs(title = "C")

(aq_miss_var | aq_miss_case) / (aq_vis_miss) / (aq_fct)

@@

Missing values can occur in the both the predictors (the "independent variables") 
and response variable (the "dependent variables"). Care should be taken 
when imputing data, as typically only predictors should be imputed. 
For discussion on imputing the response value, see ... [@refs]. **(note: take a look again - this is the discusson of missing y values section - and possible reference relevant to RCT's is this: https://doi.org/10.1191%2F1740774504cn032oa)**

>>>>

# Ampute missing values
data_ampute <- ampute(data = data[,1:3])
# try and tinker with the amount of missings - so the variables have different
# amounts of missingness
# try and introduce some missingness mechanisms

data_with_missing <- data_ampute$amp

@@

gg_miss_scatter <- ggplot(data_plot,
       aes(x = sprint_distance,
           y = sprints)) +
  geom_miss_point()

aq_miss_var <- gg_miss_var(data_plot)

cowplot::plot_grid(aq_vis_miss,
                   # aq_upset,
                   aq_fct,
                   gg_miss_scatter,
                   aq_miss_var, 
                   align = "hv",
                   labels = "AUTO")

@@

Missing values can occur in the both the predictors (the "independent variables") 
and response variable (the "dependent variables"). 
Care should be taken when imputing the outcome variables, and in general they should not be imputed with a single imputation, as this will bias the subsequent analysis.

Methods that provide multiple imputed values for the outcome, such as multiple imputation, or using a Bayesian framework that generates a distribution of posterior values, can be appropriate for imputed the outcome as they provide some sence of what the uncertainty is. For discussion on imputing the response value, see ... [@refs].

Missing values in the outcome can be dealt with specially for Randomised Control Trials, see - https://doi.org/10.1191%2F1740774504cn032oa.
